### 2021-07-12 src/paper/results/fit.tex
Remove red from some sections.

% observed infections
Our fit of the infection rates in Germany between October 2020 and June 2021 is
excellent. The incidence in our model matches both the levels and the shape of the
reported incidence almost perfectly. When the prevalence of the virus is high
\textcolor{red}{and during exponential growth phases} the effect of random events on the
incidence is large. That is why it's important that we rely on 30 simulation runs with
different seed sequences and average over these random differences to have a mean that's
robust to the randomness in our model.

@@

  \floatfoot{\noindent \textit{Note:} Both figures show averages and single runs. The
  average is the thick line. Single runs are shown as lighter and thinner lines. We
  averaged and show 30 simulation runs. The left figure shows the daily incidence rate
  per million for the reported simulated infections rates. The mean infection rate is the
  thick blue line. Single simulation runs are plotted in lighter and thinner lines. The
  official case numbers as reported by the RKI are plotted in black. The fit is overall
  very good. The higher the mean incidence and the stronger the growth the more variance
  there is between simulation runs. The right figure shows the effective replication
  number ($R_t$) as reported by the RKI and as calculated in our model. The $R_t$ gives
  the average number of new infections caused by one infected individual. The $R_t$ in
  our model broadly follows the $R_t$ reported by the RKI. Two differences stand out.
  Firstly, the RKI's $R_t$ drops faster in November. \textcolor{red}{This is likely due
  \st{to a change in the testing policy that focused tests on the elderly when the second
  wave hit Germany and led } to a decline in the estimated overall share of detected
  cases}. %when the second wave hit Germany.
  The second difference is from mid February to mid March where the RKI's reported $R_t$
  increased more rapidly than that in our model. Here the opposite effect can be
  expected. During this time rapid tests increased strongly leading to more cases being
  detected. In the short term this leads an $R_t$ estimation that is based on detected
  cases to overestimate the replication number.}
\end{figure}

>>>>

% observed infections
Our fit of the infection rates in Germany between October 2020 and June 2021 is
excellent. The incidence in our model matches both the levels and the shape of the
reported incidence almost perfectly. When the prevalence of the virus is high
and during exponential growth phases the effect of random events on the
incidence is large. That is why it's important that we rely on 30 simulation runs with
different seed sequences and average over these random differences to have a mean that's
robust to the randomness in our model.

@@

  \floatfoot{\noindent \textit{Note:} Both figures show averages and single runs. The
  average is the thick line. Single runs are shown as lighter and thinner lines. We
  averaged and show 30 simulation runs. The left figure shows the daily incidence rate
  per million for the reported simulated infections rates. The mean infection rate is the
  thick blue line. Single simulation runs are plotted in lighter and thinner lines. The
  official case numbers as reported by the RKI are plotted in black. The fit is overall
  very good. The higher the mean incidence and the stronger the growth the more variance
  there is between simulation runs. The right figure shows the effective replication
  number ($R_t$) as reported by the RKI and as calculated in our model. The $R_t$ gives
  the average number of new infections caused by one infected individual. The $R_t$ in
  our model broadly follows the $R_t$ reported by the RKI. Two differences stand out.
  Firstly, the RKI's $R_t$ drops faster in November. This is likely due to a decline in
  the estimated overall share of detected cases when the second wave hit Germany.
  The second difference is from mid February to mid March where the RKI's reported $R_t$
  increased more rapidly than that in our model. Here the opposite effect can be
  expected. During this time rapid tests increased strongly leading to more cases being
  detected. In the short term this leads an $R_t$ estimation that is based on detected
  cases to overestimate the replication number.}
\end{figure}
